# Basic Bookdown {#basic}

## R code

This is a sample r code. Just like *.rmd* file, Some code ould be embeded in line`rnorm(10)` and results is `r rnorm(10)`.

Or you can put them in a code chunk:

```{r chunk-label, fig.cap = 'A figure caption.'}
1 + 1
rnorm(10)  # 10 random numbers
plot(dist ~ speed, cars)  # a scatterplot
```

## Equations

You can even write latex into this .rmd file so to utilize the super power of latex to create complicated mathematical equations.

```latex
$$\begin{equation*} 
\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x)
\end{equation*} $$
```

$$\begin{equation*} 
\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x)
\end{equation*} $$

## Figures

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.
```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```


## Tables
```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```


## Interactive plot
```{r map, echo = FALSE}
library(grid)
library(leaflet)
Icon <- makeIcon(
        iconUrl = "https://www.columbia.edu/content/sites/default/files/styles/cu_crop/public/content/about/icon-crown.png?itok=VgCocz0Q",
        iconWidth = 31*215/230, iconHeight = 31,
        iconAnchorX = 31*215/230/2, iconAnchorY = 16
)
popup <- c("<a href='https://www.columbia.edu/'> Columbia University </a>")
location <- data.frame(
        lat = c(40.806290),
        lng = c(-73.963005)
)

location%>%leaflet()%>%addTiles()%>%addMarkers(icon = Icon, popup = popup)
```
